% Article class document
\documentclass{article}

% Setup margins (page geometry)
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=0.5in}

% Custom font
% https://tug.org/FontCatalogue/robotoslablight/
\usepackage[rm,light]{roboto}
\usepackage[T1]{fontenc}

% Automatic file modification date
\usepackage{filemod}

% Setup hyperlinks
\usepackage{hyperref}
\hypersetup{
  pdftitle={Alexander Koik-Cestone - Resume},
  % pdfborderstyle={/S/U/W 1},
  colorlinks=true,
  urlcolor=blue
}

\usepackage{xcolor}

% Sets left margin of all lists.
% Could use leftmargin= in just the itemized lists
% so that not all lists are affected by this setting.
% https://tex.stackexchange.com/questions/170525/itemize-left-margin
\usepackage{enumitem}
% \setlist{leftmargin=4.5mm}
\setlist[itemize]{
  leftmargin=1.5mm,
  topsep=0pt
  % itemsep=0pt
}

\author{Alexander Koik-Cestone}
% Using a negative vspace to reduce the top margin of the title
%\title{\texorpdfstring{\vspace{-2.0cm}}{}Resume}
\title{Resume}

\begin{document}

\begin{center}
{\huge Alexander Koik-Cestone\vspace{0.3cm}} \\
\href{https://sirkoik.github.io#portfolio}{Portfolio}
\textcolor{gray}{\textbullet}
\href{https://www.linkedin.com/in/alexander-koik-cestone-89304556/}{LinkedIn}
\textcolor{gray}{\textbullet}
\href{mailto:akoikcestone@gmail.com}{akoikcestone@gmail.com}
\textcolor{gray}{\textbullet}
\href{tel:614-674-0668}{614-674-0668} \\
%Last updated \filemodprintdate{\jobname} \\
\end{center}

\noindent
I am a software developer specializing in Appian and Microsoft Power Platform, with experience delivering upgrade-safe, enterprise-grade solutions for government and consulting clients. In Appian, I’ve developed custom record types, interfaces, process models, and audit-capable workflows, and have integrated external APIs such as Adobe Sign. I’ve also implemented multilingual interfaces and JSON-based customization. On Power Platform, I’ve built stakeholder-sensitive canvas apps, automated workflows using Power Automate and Office Scripts, and performed advanced document automation using XML manipulation. I work in agile teams, contributing to sprint delivery, test suite development, and cross-environment deployments using GitHub and Azure DevOps.

\addcontentsline{toc}{section}{Education}
\section*{Education}\vspace{-0.5em}
\begin{description}
  \item[Bachelor's of Science in Molecular and Cellular Biology] University of Arizona, 2010.
  \item[Master's of Science in Molecular and Cellular Biology] University of Arizona, 2011-2014 (partially complete)
  % \item[High School Diploma] Heidelberg American High School, 2004.
\end{description}

\addcontentsline{toc}{section}{Experience}
\vspace{-1em}
\section*{Experience}\vspace{-0.5em}
\begin{description}
  \item[Appian and Power Platform Developer] SkillStorm. Dublin, OH. Jul 2022-May 2025. \\
  Worked as an Appian and Power Platform developer for multiple clients, including Deloitte and PwC.
  \item[Appian Developer (Key Client: Deloitte)] SkillStorm. Dublin, OH. Nov 2024-May 2025. \\
  Built a contracting portal in Appian for the National Park Service by extending GAMS with upgrade-safe customizations and configurations. Managed PBIs, tests, and version control using Azure DevOps and GitHub.
  \begin{itemize}
    \item Customized and configured GAMS modules to support NPS-specific contracting workflows.
    \item Added interfaces, records, and expression rules while maintaining compatibility with upstream GAMS updates.
    \item Created auxiliary data tables for field extensions; implemented SQL INSERTs and views for efficient data access.
    \item Wrote and executed Azure DevOps test suites to validate new features and avoid regressions.
    \item Packaged deployments and tracked changes across environments using GitHub and ADO.
    \item Participated in both development and testing roles to ensure quality and maintainability.
    \item Met regularly with the client to demo, validate, and refine features based on feedback.
  \end{itemize}
  \item[Power Platform Developer (Key Client: PwC)] SkillStorm. Dublin, OH. Aug 2023-Oct 2024. \\
  Rebuilt Google App Scripts as Power Platform apps with cost-efficient automations. Developed a multi-screen enrollment app with stakeholder-aware logic using PowerFX, Dataverse, and Power Automate.
  \begin{itemize}
    \item Rebuilt Google App Scripts using Power Automate and Office Scripts to manage structured workflows and document handling.
    \item Edited Office file XML in Power Automate to update DOCX and PPTX templates without incurring platform costs related to Azure Functions.
    \item Created a stakeholder-sensitive canvas app with dynamic UI, filtered data views, and tabular summaries.
    \item Designed Dataverse tables, implemented PowerFX logic, and automated rollup field refreshes via Web API calls.
    \item Deployed solutions across multiple environments; authenticated flows and apps via Microsoft Entra.
    \item Leveraged GenAI tools to assist with development and reduce turnaround time.
  \end{itemize}
  \item[Appian Developer (Key Client: PwC)] SkillStorm. Dublin, OH. Jul 2022-Aug 2023. \\
  Redesigned an Appian-based conference scheduling system by implementing multilingual support, in-app approvals, and streamlined onboarding. Reworked process models and built modular interfaces to improve stakeholder interaction, reduce external dependencies, and enhance usability across a newly branded platform.
  \begin{itemize}
    \item Reworked form interfaces to improve usability and guide users through multi-step workflows.
    \item Created and updated process models to support new end-to-end scheduling and approval processes.
    \item Mapped Appian record types and data types from an ERD to support structured data handling.
    \item Designed MariaDB queries and stored procedures to support efficient database operations.
    \item Integrated external APIs (e.g., Adobe Sign) to enable auto-population of PDFs with relevant data.
    \item Implemented JSON-based customization templates for Appian interfaces.
    \item Modularized interface elements to enable rapid internationalization across languages.
    \item Delivered iterative feature sets under agile sprints with direct client feedback cycles.
  \end{itemize}
  \pagebreak
\item[Usability Tester] UserTesting. Dublin, OH. Nov 2016–Jun 2022.
\begin{itemize}
  \item Performed usability testing for client apps and websites.
  \item Identified bugs and design flaws; suggested improvements and novel feature ideas.
  \item Answered designer questions during one-on-one user interviews.
  \item Collaborated with designers via screen sharing tools such as Zoom.
\end{itemize}
\item[Crowd Worker] Amazon Mechanical Turk. Dublin, OH. Jan 2014–Jun 2022.
\begin{itemize}
  \item Provided user experience feedback for websites and mobile apps.
  \item Participated in A/B testing using wireframe mockups.
  \item Categorized datasets to support AI and machine learning model training for academic and corporate research.
  \item Transcribed and tagged audio and video recordings for dataset labeling and analysis.
\end{itemize}
\item[Administrative Assistant] University of Arizona Room and Course Scheduling. Tucson, AZ. Sep 2006–Apr 2010.
\begin{itemize}
  \item Analyzed university room usage data and created reports for stakeholders to optimize scheduling.
  \item Collaboratively identified areas for improvement in scheduling software and guided implementation of new features.
  \item Queried room assignment data using Microsoft Access and SQL.
  \item Used VBA to analyze spreadsheets and generate reports for staff and supervisors.
  \item Presented findings to immediate supervisors and university leadership in meetings.
\end{itemize}
\end{description}

% \pagebreak

\addcontentsline{toc}{section}{Certifications}
\vspace{-1em}
\section*{Certifications}\vspace{-0.5em}
\begin{description}
  \item [\href{https://sirkoik.github.io/CurriculumVitae/certifications/Oracle-Cloud-Infrastructure-2024-Generative-AI-Certified-Professional/Oracle-Cloud-Infrastructure-2024-Generative-AI-Certified-Professional-eCertificate.pdf}{Oracle Cloud Infrastructure 2024 Generative AI Certified Professional}] Aug 2024.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/99C5F49578EE2C21?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Power Platform Developer Associate}] Mar 2024. Renewed Mar 2025.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/34191BBB3EBF09A3?sharingId=DCF7D068E6ED12E6}{Microsoft 365 Certified: Fundamentals}] Jul 2023.
  \item [\href{https://www.credly.com/badges/f0aab7ce-2f5d-4569-8705-3dc23fc34200/public_url}{Certified in Cybersecurity (CC)}] Sep 2022.
  \item [\href{https://community.appian.com/members/alexanderk5370?badge=cert&now=638483685447952604}{Appian Certified Senior Developer}] Sep 2022. Renewed 2025.
  \item [\href{https://community.appian.com/members/alexanderk5370?badge=cert&now=638483685447952604}{Appian Certified Associate Developer}] Aug 2022. Renewed 2025.
  \item [\href{https://community.appian.com/members/alexanderk5370?badge=cert&now=638483685447952604}{Appian Certified Analyst}] Jul 2022. Renewed 2025.
  \item [\href{https://www.credly.com/badges/e75210e4-8d08-43ea-af72-ec70ef666eee/public_url}{[JSE-40-01] JSE – Certified Entry-Level JavaScript Programmer}] Dec 2021.
  \item [\href{https://api.badgr.io/public/assertions/KE5P9gfoQ7S3-hpvZP4PIQ}{Lean Six Sigma Yellow Belt Certification}] May 2022.
  \item [\href{https://api.badgr.io/public/assertions/JhPP0s2rQWWGrc9ZkYqhkg}{Lean Six Sigma White Belt Certification}] Feb 2022.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/DF45C662407C41C5?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Security, Compliance, and Identity Fundamentals}] Mar 2022.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/37294D69297F1741?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Azure Data Fundamentals}] Feb 2022.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/CE492D7BE04E2F0D?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Power Platform Fundamentals}] Feb 2022.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/51E3A61AEA2E3998?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Azure Fundamentals}] Jan 2022.
  \item [\href{https://learn.microsoft.com/api/credentials/share/en-us/AlexKoikCestone-7541/32EE850D92B0C609?sharingId=DCF7D068E6ED12E6}{Microsoft Certified: Azure AI Fundamentals}] Dec 2021.
\end{description}

\addcontentsline{toc}{section}{Skills}
\vspace{-1em}
\section*{Skills}\vspace{-0.5em}

\begin{itemize}
  \item \textbf{Databases:} SQL (INSERTs, stored procedures, views), MySQL, Dataverse\\
  \textit{Versioned inserts and updates tracked via GitHub}
  
  \item \textbf{Appian Development:} Record Types, Interfaces, Process Models, Expression Rules, Deployment Packages
  
  \item \textbf{Microsoft Power Platform:} Canvas Apps, Power Automate, Dataverse\\
  \textit{Built multi-screen apps with role-based views and automated document workflows}
  
  \item \textbf{Frontend Development:} React (Hooks, Context API, Reducers), HTML5, CSS3, JavaScript (ES6), TypeScript\\
  \textit{UI state managed with reducers; modular components with responsive design}
  
  \item \textbf{DevOps / Version Control:} Git, GitHub (SQL change tracking, JSON templating), Azure DevOps (Kanban, PBIs, story points, test cases, pipelines)
  
  \item \textbf{Collaboration:} Agile, Scrum, MS Teams (cross-org coordination), Daily Standups, Client Demos, QA Syncs\\
  \textit{Regular demos to stakeholders; feedback loop integrated into sprint cycles}
  
  \item \textbf{Quality and Testing:} Test Script Authoring and Execution, Usability Testing, A/B Testing, Lighthouse Audits

  \item \textbf{Security:} XSS/SQL Injection Prevention, Password Salting, MFA, SSO (Azure AD)
\end{itemize}

\vspace{0.5em}
\subsection*{Additional Tools and Experience}
\begin{itemize}
  \item VBA, Firebase, XML, Markdown, \LaTeX\footnote{\href{https://github.com/sirkoik/CurriculumVitae/blob/master/source/main/resume.tex}{Resume source}}, Blender
  \item Codewars: \href{https://www.codewars.com/users/sirkoik}{125+ katas} in JavaScript, Java, Python, SQL
  \item LinkedIn Skill Badges: HTML, CSS, React, JSON, JavaScript, PHP, MySQL, VBA
\end{itemize}

\addcontentsline{toc}{section}{Portfolio}
\vspace{-0.5em}
\section*{Portfolio}\vspace{-0.5em}

\begin{description}
  \item[Authored apps]
  \item[Piedmont Insurance] Portfolio Appian application which handles insurance policy selection and management workflows involving multiple company stakeholders.
  \item[Precision Loan Group] Portfolio Appian application which handles a loan application and approval workflow with multiple involved stakeholders. 
  \item[\href{https://sirkoik.github.io/Celestial-Compare}{Celestial Compare}] React-based planetary body comparison app. Skills: React, React hooks.\\ \href{https://sirkoik.github.io/Celestial-Compare}{Live site} \textcolor{gray}{\textbullet} \href{https://github.com/sirkoik/Celestial-Compare}{Source code}
  \item[\href{https://sirkoik.github.io/BorisovXmas}{Comet 2P/Borisov}] Narrated tale about comet 2P/Borisov. Skills: HTML, CSS, JavaScript, webpack. \\ \href{https://sirkoik.github.io/BorisovXmas}{Live site} \textcolor{gray}{\textbullet} \href{https://github.com/sirkoik/BorisovXmas}{Source code}
  \item[\href{https://sirkoik.github.io/FallingObjects}{A Snowy Day}] Fully 3D, interactive web-based snowfall animation. Skills: HTML, JavaScript, ThreeJS, Rollup, Blender. \\
  \href{https://sirkoik.github.io/FallingObjects}{Live site} \textcolor{gray}{\textbullet} \href{https://github.com/sirkoik/FallingObjects}{Source code}
  \item[\href{https://sirkoik.github.io/February}{Valentine's Day card}] Animated Valentine's Day greeting card app with customizable message. \\
  Skills: HTML, JavaScript, ThreeJS, Blender. \href{https://sirkoik.github.io/February}{Live site} \textcolor{gray}{\textbullet} \href{https://github.com/sirkoik/February}{Source code}   
  \item[Sample usability tests:] \href{https://youtu.be/n0ts2tmBpzI}{Desktop}, \href{https://youtu.be/935ftL_X_rY}{Mobile app}
\end{description}

% \noindent
% non-breaking space = ~
% \begin{description}
%   \item [Currently studying for] ~
%   \begin{itemize}
%     \item 
%   \end{itemize} 
% \end{description}

\addcontentsline{toc}{section}{Classes and Conferences}
\vspace{-1em}
\section*{Classes and Conferences}\vspace{-0.5em}
\begin{description}
  \item [Appian Academy] Jul 2022-. Mastered the concepts of Appian group security, data types, record types, data stores, expression rules, interfaces, constants, and integrations with other platforms such as Salesforce. Mastered the concepts of Appian deployment and testing. Gained full knowledge of Appian's system architecture such as its execution and analytics engines, the Apache Tomcat server and the static Apache webserver.
  \item [Microsoft Security Virtual Training Day: Security, Compliance, and Identity Fundamentals] Feb 2022. Mastered the concepts of privacy, security, and governance in Azure. Mastered the concepts of multi-factor authentication (MFA), conditional access, privileged identity management (PIM), and zero trust. Mastered the concepts of regulatory and business policy compliance enforcement, eDiscovery, and auditing. Mastered the usage of Microsoft Defender for Cloud, Microsoft Service Trust Portal, Microsoft 365 Defender portal, Microsoft Sentinel, Microsoft Defender for Office 365, Microsoft Security and Compliance Center, Microsoft Endpoint Manager, and Intune. Achieved \href{https://www.credly.com/badges/606ab01b-911d-4408-a6a8-303b121d4fc8/public_url}{Microsoft Certified: Security, Compliance, and Identity Fundamentals} in Mar 2022.
  \item [Microsoft Power Platform Virtual Training Day: Fundamentals] Jan 2022. Mastered the fundamentals of the Microsoft Power Platform, including Power Automate and Power BI. Mastered the fundamentals of low-code and no-code apps. Gained competency in the concepts of canvas apps, model-driven apps and portals, as well as the Microsoft Dataverse and the Common Data Model. Mastered the fundamentals of the Power BI desktop and its utility in deriving business intelligence insights. Gained competency in structuring and sharing apps with colleagues and supervisors in a manner that places regulatory compliance and Data Loss Prevention at the forefront. Achieved \href{https://www.credly.com/badges/eeabb8f3-4c51-431e-9174-1528f4ecd6d3/public_url}{Microsoft Certified: Power Platform Fundamentals} in Feb 2022.
  \item [Microsoft Azure Virtual Training Day: Data Fundamentals] Dec 2021. Mastered the fundamentals of data including transactional and analytical data, roles in data, non-relational data and data analytics. Gained mastery of non-relational data fundamentals, such as JSON-based data and graph databases, Azure offerings such as Azure Table Storage, Azure Blob Storage, and Azure Cosmos DB. Mastered the usage of relational Azure data services such as Azure SQL Server, Azure SQL DB, Azure SQL Managed Instance, and Azure servers for MySQL, PostgreSQL, and MariaDB. Gained competency querying SQL, provisioning databases, and using Role-Based Access Control (RBAC) on Azure. Mastered the fundamentals of data warehousing, such as data ingestion, data processing, and data exploration, including the usage of Azure Synapse Analytics, Azure Databricks and Power BI. Achieved \href{https://www.credly.com/badges/677cac34-dc29-4535-ba97-6d4c81ccf19e/public_url}{Microsoft Certified: Azure Data Fundamentals} in Feb 2022.
  \item [Microsoft Azure Virtual Training Day: DevOps with GitHub] Dec 2021. Mastered the fundamentals of DevOps and its use with Github and Microsoft Teams as a collaboration hub. Mastered the scrum process and continuous integration / continuous delivery (CI/CD). Mastered GitHub Secrets and Azure Key Vault. Mastered the fundamental concepts of code quality, security, and containerization. Mastered the fundamentals of Kubernetes and container orchestration, including its integrations with Azure and Azure Policy. Mastered the fundamentals of logic apps.
  \item [Microsoft Azure Virtual Training Day: AI Fundamentals] Nov 2021. Mastered the fundamentals of AI and its use with the Azure platform. Learned about computer vision, machine learning, Azure's Natural Language Processing, and conversational AI and bot tooling. Learned about AI basics such as training sets, validation sets, and the confusion matrix. Learned about supervised and unsupervised learning, and how Azure can automate machine learning by selecting the most optimal algorithms. Learned about Azure's Cognitive Services such as the Computer Vision Service and how they can be consumed with REST APIs. Learned about speech recognition and Language Understanding (LUIS). Learned about the challenges and risks associated with AI and how to use it in a responsible manner. Achieved \href{https://www.credly.com/badges/fa66cf6b-dff5-4f58-9f4e-4b94fc91b7fa/public_url}{Microsoft Certified: Azure AI Fundamentals} in Dec 2021.
  \item [Microsoft Azure Virtual Training Day: Fundamentals] Nov 2021. Mastered the fundamentals of Microsoft Azure, including availability options, resource groups, the resource manager, subscriptions, VMs, app services, serverless computing, container services and Kubernetes, Windows Virtual Desktop, Azure Database Service, the Defense in Depth model and Network Security Groups, the Azure firewall and DDoS protection, Azure identity services, Role-Based Access Control, resource locks, tags, Azure policy, Azure Blueprints, the Cloud Adoption Framework, Compliance, the Azure Trust Center, data governance, pricing and SLAs. Achieved \href{https://www.credly.com/badges/56339905-a587-4fdb-9906-c2d2bb5d31da/public_url}{Microsoft Certified: Azure Fundamentals} in Jan 2022.
  \item [Microsoft Security Virtual Training Day: Secure and Protect Your Organization] Oct 2021. Learned about how to secure and protect Microsoft 365 enterprise and hybrid environments, proactively manage security threats, manage data governance, and control device use.
  \item [\href{https://www.linkedin.com/posts/alexander-koik-cestone-89304556_alexander-koik-cestones-nextjs-conf-ticket-activity-6855242508260184065-xJP9/}{NextJS Conf 2021}] Oct 2021. Learned about NextJS 12 and edge functions. Watched speakers from various companies such as Invision talk about how NextJS helped both their developer and user experience.
  \item [\href{https://sirkoik.github.io/CurriculumVitae/certifications/Nodejs-The-Big-Picture/certificate.pdf}{Node.JS: The Big Picture}] Sep 2021. Reached medium competency in NodeJS.
  \item [\href{https://www.udemy.com/certificate/UC-2196f0cf-2dce-4a11-9d8e-421827506ad1/}{React - The Complete Guide}] Sep 2021. Mastered ReactJS, hooks, authentication, Redux, REST APIs, MongoDB, and NextJS. Completed several class projects.
  \item [\href{https://sirkoik.github.io/CurriculumVitae/certifications/Agile-for-One/certificate.pdf}{Agile for One}] May 2021. Learned basic Agile and Scrum techniques for managing projects. Incorporated Agile and Scrum methodologies with Trello.
  \item [\href{https://sirkoik.github.io/CurriculumVitae/certifications/certificate-of-completion-for-git-github-the-practical-guide.pdf}{Git \& Github - The Practical Guide}] Dec 2020. Learned the basics of both Git and Github.
  \item [\href{https://www.udemy.com/certificate/UC-624f6f83-940e-428f-accd-d16113661ded}{Angular - The Complete Guide (2020 Edition)}] Oct 2020. Mastered Angular, RxJS, NgRx, routes, guards, REST API endpoints. Completed numerous class projects.
  \item [\href{https://www.udemy.com/certificate/UC-E3EMJE4O}{Complete AJAX Using Bootstrap, PHP from Basic to Advanced}] Apr 2018. Mastered creating a basic website or web app with AJAX, the Bootstrap framework, and PHP.
  \item [\href{https://www.udemy.com/certificate/UC-QZDWYX3V}{The Complete HTML \& CSS Course, From Novice to Professional}] Apr 2017. Became skilled at writing HTML and CSS-based web front-ends.
  \item [\href{https://www.udemy.com/certificate/UC-4V285L2N}{Complete jQuery and jQuery UI Course for Beginner}] Dec 2016. Learned about jQuery.
  \item [CSC 227 - Program Design and Development] University of Arizona, August 2008. Mastered primitives and arrays, basic control structures, recursion, linked structures, binary trees, and hashing in Java. This was the equivalent of CSC 127 A and B, or a year's worth of study combined into one intensive class. Received an A in the class.
  \item [AP Computer Science A] May 2004. Mastered loops, data structures, linked lists, and object oriented programming concepts. Scored a 4 on the AP test.
\end{description}

\addcontentsline{toc}{section}{References}
\vspace{-1em}
\section*{References}\vspace{-0.5em}
\begin{description}
  \item [\href{https://www.linkedin.com/in/moeezsheikh/}{Moeez Sheikh}] Mentored me in advanced Appian development, with a focus on upgrade-safe design patterns, performance optimization, and efficient implementation strategies. Provided expert guidance on best practices for scalable development and safe deployment across environments. 
  \item [\href{https://www.linkedin.com/in/joespain/}{Joe Spain}] Talent Developer, SkillStorm. Jul 2022-May 2025. Enabled me to master the Appian platform and guided me as I developed Appian applications as part of an Agile team.
\end{description}

\end{document}