%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{xspace}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
urlcolor=blue,
filecolor=blue
}
% Change footnote text
% https://tex.stackexchange.com/questions/826/symbols-instead-of-numbers-as-footnote-markers#830
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\namesection{Alexander}{Koik-Cestone}{
%\namesection{}{Alexander Koik-Cestone}{
\begin{center}
{\Huge Alexander Koik-Cestone} \\
\urlstyle{same}Website \href{https://sirkoik.github.io}{\underline{sirkoik.github.io}} | 
\href{https://www.linkedin.com/in/alexander-koik-cestone-89304556/}{\underline{LinkedIn}} \\
\href{mailto:akoikcestone@gmail.com}{\underline{akoikcestone@gmail.com}} |  \href{tel:614-674-0668}{\underline{614-674-0668}} \\
Last updated on October 22, 2021
%}
\end{center}

%\href{https://www.linkedin.com/in/alexander-koik-cestone-89304556/}{\underline{https://www.linkedin.com/in/alexander-koik-cestone-89304556/}}

%\begin{center}
%\huge\color{subheadings}\custombold{Biology and Programming}
%\end{center}

%\sectionsep

\sectionsep
\location{I am a professional with experience in detail-oriented data analysis work,  usability testing and programming.}
\sectionsep

\section{Education}
\runsubsection{University of Arizona}
\descript{| Bachelor of Science in Molecular and Cellular Biology}
\location{College of Arts and Sciences | Jan 2006 - Dec 2010 | Tucson, AZ}
\sectionsep

\runsubsection{University of Arizona}
\descript{| Additional Biology Classes}
\location{College of Arts and Sciences | Aug 2011-Jan 2012 | Tucson, AZ}
\sectionsep

\section{Experience}

\runsubsection{UserTesting}
\descript{| User Experience Analyst }
\location{Nov 2016 – present | Dublin, OH}
\begin{tightemize}
\item Analyze websites and apps for user experience problems for many clients and make suggestions about where their design could be improved.
\item Identify bugs or malfunctions in app and website designs.
\item Identify areas where apps and websites were well-designed and provide suggestions for novel features that could be added.
\item Interact with designers using both screencasting and Zoom.
\end{tightemize}
\sectionsep

\runsubsection{TestBirds}
\descript{| User Experience Analyst }
\location{Nov 2016 - present | Dublin, OH}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Perform app and website usability testing for many clients.
\item Write reports outlining steps taken during the test.
\item Document bugs in a detailed fashion with screenshots, video recording, and written description.
\end{tightemize}
\sectionsep

\runsubsection{Amazon, Crowdsurf}
\descript{| Data categorization, Writing, and Transcription}
\location{Jan 2014 - present | Dublin, OH}
\begin{tightemize}
\item Provide user experience feedback for websites and apps, including participating in A/B tests with wireframe mockups.
\item Provide survey data, including Written content for corporate and academic institutions.
\item Transform ideas and concepts into human-readable written text.
\item Categorize data to train AI and ML models.
\item Participate in paid pilot experiments for academic, scientific, and corporate institutions.
\item Transcribe audio and video conversations, interpreting and tagging them appropriately.
\end{tightemize}
\sectionsep

\runsubsection{Appen}
\descript{| Usability consulting, Fact checking}
\location{Jan 2019 - present | Dublin, OH}
\begin{tightemize}
\item Provide usability and content relevancy feedback for corporate institutions.
\item Work as a fact checker, investigating claims on social media posts for accuracy. (Late 2020)
\end{tightemize}
\sectionsep

\runsubsection{University of Arizona Room and Course Scheduling}
\descript{| Administrative Assistant / Intern}
\location{Aug 2006 – May 2007, Aug 2009 - May 2010 | Tucson, AZ}
\begin{tightemize}
\item Wrote SQL queries and created reports from tables in the course scheduling database. Directly queried PeopleSoft database in custom report macros.
\item Used software such as Microsoft Access to prepare reports that assisted in room assignment decision making.
\item Participated in regular meetings with fellow students, superiors, and university officials discussing scheduling needs.
\item Developed VBA macros to streamline the scheduling report process.
\end{tightemize}
\sectionsep

\runsubsection{Freelance projects}
\descript{}
\location{2010-}
\begin{tightemize}
\item Develop websites on a freelance basis.
\item Use of technologies like HTML, CSS, and JQuery on the client side, and PHP and MySQL on the server side.
\item Use of Apache Web Server and MySQL server.
\item Deploy to website hosting with domain name services.
\end{tightemize}
\sectionsep

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS AND CLASSES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications and classes}
\runsubsection{Node.js: The Big Picture}
\descript{| \href{https://sirkoik.github.io/CurriculumVitae/certifications/Nodejs-The-Big-Picture/certificate.pdf}{\underline{Pluralsight, Sep 2021}}}
Learned about the NodeJS event loop, event emitters, streams, Node Package Manager (npm), and testing with Mocha and Chai.
\sectionsep

\runsubsection{React - The Complete Guide (incl Hooks, React Router, Redux)}
\descript{| \href{https://www.udemy.com/certificate/UC-2196f0cf-2dce-4a11-9d8e-421827506ad1/}{\underline{Udemy, Sep 2021}}}
Learned how to write dynamic websites using the React library, and how to use libraries like Redux and NextJS.
\sectionsep

\runsubsection{React: The Big Picture}
\descript{| \href{https://sirkoik.github.io/CurriculumVitae/certifications/React-The-Big-Picture/certificate.pdf}{\underline{Pluralsight, May 2021}}}
Learned about the basics of the React library and how it compares to frameworks like Angular, Vue, and Ember.
\sectionsep

\runsubsection{Agile for One}
\descript{| \href{https://sirkoik.github.io/CurriculumVitae/certifications/Agile-for-One/certificate.pdf}{\underline{Pluralsight, May 2021}}}
Learned basic Agile and Scrum techniques for managing projects. 
\sectionsep

\runsubsection{Git \& Github - The Practical Guide}
\descript{| \href{https://sirkoik.github.io/CurriculumVitae/certifications/certificate-of-completion-for-git-github-the-practical-guide.pdf}{\underline{Academind, Dec 2020}}}
Learned the basics of both Git and GitHub.
\sectionsep

\runsubsection{Angular - The Complete Guide (2020 Edition)}
\descript{| \href{https://www.udemy.com/certificate/UC-624f6f83-940e-428f-accd-d16113661ded/}{\underline{Udemy, Oct 2020}}}
Learned how to create dynamic websites using the Angular framework.
\sectionsep

\runsubsection{Complete AJAX Using Bootstrap, PHP from Basic to Advanced}
\descript{| \href{https://www.udemy.com/certificate/UC-E3EMJE4O/}{\underline{Udemy, Apr 2018}}}
Learned AJAX, Bootstrap CSS, and the PHP programming language.
\sectionsep

\runsubsection{The Complete HTML \& CSS Course, From Novice to Professional}
\descript{| \href{https://www.udemy.com/certificate/UC-QZDWYX3V/}{\underline{Udemy, Apr 2017}}}
Learned the HTML and CSS languages for writing website front-ends.
\sectionsep

\runsubsection{Complete jQuery and jQuery UI Course for Beginner}
\descript{| \href{https://www.udemy.com/certificate/UC-4V285L2N/}{\underline{Udemy, Dec 2016}}}
Learned how to use jQuery, a dynamic JavaScript framework for web pages.
\sectionsep

\section{Classes in progress}
\runsubsection{NextJS}
\descript{| Udemy}
Learning about the NextJS library in-depth.
\sectionsep

\runsubsection{NodeJS}
Learning NodeJS.
\sectionsep

\section{Skills}
\runsubsection{Basic skills}
\descript{}
\begin{tightemize}
\item Microsoft Office: Word\footnotemark, Excel\footnotemark[\value{footnote}], PowerPoint, Access (10 years of experience)
\item Zoom: Collaboration, breakout rooms, screen sharing (3 years of experience)
\item Trello (1 year of experience)
\item OneDrive, Google Drive, cloud storage (5 years of experience)
\item Todoist (collaborative task management system) (5 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{User Experience}
\descript{}
\begin{tightemize}
\item Usability testing of apps and websites (5 years of experience)
\item Bug hunting and submitting bug reports (5 years of experience)
\item Highlighting well-designed parts of apps and websites (5 years of experience)
\item Suggesting usability changes in areas where improvements are needed (5 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Transcription and Content Categorization}
\descript{}
\begin{tightemize}
\item Amazon Mechanical Turk (5 years of experience)
\item Video and Audio Transcription (5 years of experience)
\item Categorization of items to train Machine Learning algorithms (5 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Fact Checking}
\descript{}
\begin{tightemize}
\item Fact checking political and medicine-related social media posts and videos (1 year of experience)
\item Investigating claims to make sure that they are backed up by reputable sources (1 year of experience)
\item Rating posts on how true or false they are, in part and in aggregate (1 year of experience)
\end{tightemize}
\sectionsep

\newpage

\section{Skills (Programming / Development)}
\runsubsection{Projects}
\descript{}
\begin{tightemize}
\item \href{https://sirkoik.github.io#projects}{\underline{\textcolor{blue}{sirkoik.github.io}}} has all projects.
\end{tightemize}
\sectionsep

\runsubsection{Development}
\descript{}
\begin{tightemize}
\item Front-end Development\footnotemark[\value{footnote}] (5 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Programming / Scripting languages}
\descript{}
\begin{tightemize}
\item JavaScript\footnotemark[\value{footnote}]: ES5, ES6 (10 years of experience)
\begin{itemize}
\item PluralSight Skill IQ: \href{https://app.pluralsight.com/profile/alexander-koik-cesto}{\underline{Proficient (174)}}
\end{itemize}
\item React\footnotemark[\value{footnote}], Redux, Redux Toolkit, Redux DevTools, React Developer Tools, Styled Components (one year of experience)
\item Webpack (module bundler) (1 year of experience)
\item Jasmine (1 year of experience)
\item Angular\footnotemark[\value{footnote}], NgRx, RxJS (2 years of experience)
\item TypeScript (2 years of experience)
\item jQuery\footnotemark[\value{footnote}] (10 years of experience)
\item ThreeJS (5 years of experience)
\item Java (3 years of experience)
\item PHP\footnotemark[\value{footnote}] (10 years of experience)
\item \LaTeX \xspace (used for this r\'esum\'e) (1 year of experience)
\item Perl (1 year of experience)
\item GenBank (1 year of experience)
\item VBA\footnotemark[\value{footnote}] (2 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Optimization}
\descript{}
\begin{tightemize}
\item Lighthouse
\end{tightemize}
\sectionsep

\runsubsection{Backends}
\descript{}
\begin{tightemize}
\item Firebase (1 year of experience)
\item Use of REST APIs (2 years of experience)
\item NodeJS (basic use, 2 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Databases}
\descript{}
\begin{tightemize}
\item MySQL\footnotemark[\value{footnote}] (5 years of experience)
\item SQL: databases, basic queries, joins and aggregate queries, performance optimization (5 years of experience)
\item PeopleSoft (2 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Markup languages}
\descript{}
\begin{tightemize}
\item HTML5\footnotemark[\value{footnote}] (10 years of experience)
\begin{itemize}
\item PluralSight Skill IQ: \href{https://app.pluralsight.com/profile/alexander-koik-cesto}{\underline{Expert (205)}}
\end{itemize}
\item CSS\footnotemark[\value{footnote}], CSS3 (10 years of experience), SASS/SCSS (1 year of experience)
\item XML (5 years of experience)
\item JSON\footnotemark[\value{footnote}] (5 years of experience)
\item Frameworks: Bootstrap (1 year of experience)
\end{tightemize}
\sectionsep

\runsubsection{IDEs}
\descript{}
\begin{tightemize}
\item Microsoft Visual Studio Code (2 years of experience)
\item IntelliJ IDEA
\item Brackets (2 years of experience)
\end{tightemize}
\sectionsep

\runsubsection{Version Management}
\descript{}
\begin{tightemize}
\item Git (3 years of experience)
\item \href{https://github.com/sirkoik}{\underline{GitHub}} (3 years of experience)
\item Atlassian BitBucket (2 years of experience)
\end{tightemize}
\sectionsep

\footnotetext{Earned LinkedIn Skill Assessment Badge}

\newpage

\section{Training}
% \descript{}
\runsubsection{Ongoing training and learning}
\descript{}
\begin{tightemize}
\item \href{https://app.pluralsight.com/profile/alexander-koik-cesto}{\underline{Pluralsight profile}} which also has information about skills proficiency.
\item \href{https://www.codewars.com/users/sirkoik}{\underline{Codewars}} currently at 5 kyu.
\end{tightemize}
\sectionsep

%\section{Languages}
%\begin{minipage}[t]{.6\textwidth}
%\subsection{Programming}
%\location{Over 5000 lines:}
%JavaScript \textbullet{} Shell \textbullet{} VBA \\ 
%\location{Over 1000 lines:}
%C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} VBA \\
%\location{Familiar:}
%AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
%\sectionsep
%\end{minipage}
%\hfill
%\begin{minipage}[t]{.35\textwidth}
%\subsection{Spoken \& Written}
%\location{Native fluency:} English\\
%\end{minipage}

\end{document}  \documentclass[]{article}